A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-08-08 response_letter.tex

\documentclass[12pt,letterpaper]{article}
\usepackage{url}
\usepackage{color}
%\signature{Your name}
%\address{Cooperage Building \\ North Mall Campus \\ University College Cork \\ Cork \\ Ireland}
\begin{document}
%\begin{letter}{Company name \\ Street\\ City\\ Country}
Dear Miguel Ara\'{u}jo,

@@

\begin{enumerate}
\item{Abstract: Scavenging can be difficult to observe, but probably no more so than predation.
Also, using experimental carcasses, scavenging is actually quite easy to observe.}

\textcolor{blue}{We emphasise that food webs have tended to lump all carnivory into predation and it is with extinct species that we have no observational evidence.}

\item{Abstract: You should point out that your ``scale of scavenging'' is only qualitative; you made no attempt to quantify such traits.}

\textcolor{blue}{We now clearly state that the scale is qualitative.}

@@

\item{Introduction: Much of this section seems to follow DeVault's (2003) review paper on scavenging—in fact, there is almost nothing new here that is not covered in that earlier review.}

\textcolor{blue}{We have rewritten the introduction to more accurately reflect the aim of this review i.e. that the scavenging gradient allows us to infer scavenging in the fossil record as well as in modern species.} %TG:

@@

\item{I think that early on in the paper you need to define obligate and facultative scavengers and then throughout the paper, specify which you are referring to. For example, in the first sentence of the Detection section, you talk about ``known scavengers'', but it is unclear if you really mean obligate scavengers. Nearly all carnivorous vertebrates are scavengers at least to some extent, so you need to elaborate on what you mean when you talk about ``scavengers''.}

\textcolor{blue} {We make the following point in our introduction: \textit{``Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient. Even vultures, the canonical example of obligate scavengers, can hunt.''} We have tried to be clearer throughout the paper as well.}

\item{Last sentence of Introduction: Again, you propose a ``scale of scavenging'', but without quantification, it is unclear how useful this ``scale'' is.}

\textcolor{blue}{See the point above which highlights that the concept of a scale, and not a false caterogisation, is central to our paper. We have now clarified one of the advantages of such a scale at the end of the introduction: \textit{``We argue that such a scale could be valuable when behaviour can not be observed directly, e.g. for extinct vertebrates.''}}

@@

\item{Page 6, 12: In your discussion of aquatic scavengers, you might want to refer to Beasley et al. (2012; Oikos 121:1021-1026).}

\textcolor{blue}{We have included this reference and explicitly discuss how differences in the physical properties of water Vs air can affect scavenging: \textit{``The physical differences between water and air mean carcass availability is radically different between these environments (Beasley et al. 2012). For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers. Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers (Beasley et al. 2012). Research has shown that an animal need only travel between 16 to 36 km to encounter a fresh whale carcass  (Mole\'{o}n and Sánchez-Zapata 2015). The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.''}}

\item{Page 6: Why is jaw morphology likely to define scavengers?  Please elaborate.}

\textcolor{blue}{We've removed the reference to jaw morphology here because this section is about locomotion.}
%TG: Note that there's no change in the text here. Just a lecture on jaw morphologies. We might want to elaborate a bit in the manuscript.

@@

\item{Page 9: It is true that carrion can comprise a large percentage of a hyena's diet, but your text seems misleading. Most studies have shown that most of a hyena's diet is from predation. For example, see Cooper et al. (1999; Afr. J. Ecol. 37:149–160) and Gasaway et al. (1991; Afr. J. Ecol. 29: 64–75).}

\textcolor{blue}{We have clarified this point about hyenas to say it is their ability to take large proportions of carrion under certain circumstances that makes them a useful focal species: \textit{``The particular ability of hyenas to subsist on high proportions of carrion means we can use them as examples of efficient terrestrial scavengers to compare with other forms.''}}

\item{Your section on Handling Time is so short that I think it should be cut or combined with another section.}

\textcolor{blue}{The hierarchy of our paper wasn't clear as we intended in the first version but thanks to the review process we have now clarified that this is the lead in to a larger section which has subsections e.g. food processing (see also updated figure 1).}

@@

\end{enumerate}

\section{Reviewer: 2}
This article is a review of the literature what the authors term a ``natural history'' of scavenging.
They have approached the topic from the perspective of ecological variables (and other variables that condition them) in optimal foraging theory including encounter rate and handling time, but also metabolism, locomotion (e.g soaring and swimming), detection, prey availability, competition, and food processing.
They describe many useful examples of the behavior and ecology of obligate and facultative scavengers.
But I think they often go to far in their assumptions in trying to weave these examples together in a synthetic way.
Some examples are inferring scrounging behaviors in flying pterosaurs (pace 11), assuming that hominins used vultures to identify scavenging opportunities (page 11), surmising that scavenging evolved with the earliest tetrapods based on ``potential carrion unexploited by marine vertebrates'' (page 12).
There is a lot of ``these researchers have suggested X'' and then taking that as a given fact.

\smallskip
\textcolor{blue}{One of the central points of our paper is to compare the biology of extant scavengers with extinct species in order to determine if they were suited to scavenging.
And as we discuss in our introduction, because we can't observe the behaviour of extinct species directly we are left to make assumptions about their behaviour. 
Rather than taking them as fact we offer these as possible behaviours that the extinct species engaged in.
We have added some extra references in support of our claims e.g. \textit {``Thus, given pterosaurs seem to have cohabited in large numbers (Witton 2013), and the theoretical benefits this can have for social foraging in birds (Dermody et al. 2011), it seems probable that scrounging behaviours were seen in the flying pterosaurs as well.''}}

% All of the examples we use are backed up by references from previous work.
% But this is hardly unique to our work.

@@

\smallskip

While the authors distinguish between obligate and facultative scavenging, they tend to lump them together when it comes to constructing their arguments.
In the end, is the argument about the former, or the latter? Is the real interest in whether species scavenge at all, what proportion of their resources are obtained by scavenging, or what the conditions are that produce facultative or obligate scavengers?

\textcolor{blue} {This was also raised by reviewer 1.
We make the following point in our introduction: \textit{Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient. Even vultures, the canonical example of obligate scavengers, can hunt.} We have tried to be clearer throughout the paper as well. Indeed, this is a key point of our review paper: to change our view of scavenging from the classic dichotomy of obligate and facultative scavengers, to a sliding scale depending on the species and the ecosystem. }

@@

They also seem to ignore flexibility in species' behaviors.
For instance, while spotted hyenas are on their highly scavenging side of their Figures 1 and 2, in some ecosystems they hunt significant proportion of their prey.
Similarly, lions can take a large proportion of their prey as scavenged, as the authors note.
But to suggest, as they do in their abstract, that they can apply their scale of scavenging to any species at any time to judge how important scavenging was in its diet is frankly completely ignoring behavioral variability over time and space. 
\smallskip

\textcolor{blue}{It is certainly true that scavengers can be variable in the proportion of carrion they consume but we would argue that species like hyenas have certain characteristics that make this possible.
In contrast, cheetahs do not have a biology that lends itself to scavenging in the wild, due to poor competitive ability etc.
We appreciate that there is a continuum across and among species which we specifically note in this revised version. 
As we note in the above comment, a combination of a species traits, and the state of the ecosystem they find themselves in will determine their scale of scavenging. 
Search rates can be altered by environmmetal or ecological conditions as well as intrinsic traits of the forager. 
So, far from invalidating our idea it reinforces it.
Moreover, researchers working in palaeobiology often try to reconstruct the behaviours of extinct species; we are following this approach when we make inferences about ancient systems.}
\smallskip

@@

It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way.
Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors.
Diversity has specific ecological definition(s) that are being ignored here.

\textcolor{blue}{Figure 2 has been removed and figure 1 has been expanded.}

%TG: They make a point here (although their diversity definition rant is completely out of topic). Should we just drop figure 2 and use it as an abstract/press release picture? AK Agreed

@@

\smallskip
In sum, while I think the aim of the article is a very worthwhile one, I think the authors cannot claim to have produced an all-encompassing model that can predict the presence or level of scavenging in any organism - because I think this simply cannot be done.

%TG: State somewhere here as a response to the reviewer that we don't develop any model in this paper?

Finally, some of the perspectives of this manuscript overlap substantially with parts of Beasley et al. 2015 (pages 108-112), which is cited numerous times in the manuscript.
\smallskip

\textcolor{blue}{The sections of Beasley et al. (2015) are: 1. the evolution of scavengers, 2. competition between scavengers and 3. environmental effects on scavenger ecology.
These are very broad areas so in a review of this sort some overlap is inevitable.
We feel our inclusion of extinct species and systems as well as the novel framing under optimal foraging theory gives this manuscript its novelty.} 
\smallskip

@@

\textcolor{blue}{We have reworded this section to make the more general point that ambush predators can rely more on hunting than can cursorial species, a point explicitly stated in the Pereira et al. (2014) article, which we now cite.}

 Page 11, 1st sentence: see Kane et al. (2014) and Mole\'{o}n et al. (2014 Biol. Rev.) for inter-specific interactions.\\
 Page 11, 4th sentence: Kane et al. (2014) is not appropriate here because it is about inter-specific interactions; use Cort\'{e}s-Avizanda et al. (2014) instead.\\
 Page 14, 2nd paragraph, 1st sentence: see also Mole\'{o}n et al. (2014 Biol. Rev.) and Pereira et al. (2014).\\
 Page 14, 2nd paragraph, 2nd sentence: see better Pereira et al. (2014) and P\'{e}riquet et al. (2015). \\
 Page 14, bottom paragraph, 3rd sentence: you may also consider Moreno-Opo et al. (2016).\\
 Page 15, 2nd paragraph, 2nd sentence: see also Mole\'{o}n et al. (2014 Biol. Rev.) and Pereira et al. (2014).

\textcolor{blue}{All of these references have been added.}

\item{You should include more discussion about the importance of carcass size throughout the ms, as it has a strong influence on scavenging patterns and interactions among vertebrates and between vertebrates and smaller carrion consumers (e.g., see Mole\'{o}n et al. 2015).}

\textcolor{blue}{We have included a new section detailing the influence of carcass size on scavenger ecology \textit{``Modern scavenging assemblages are known to be influenced by carcass size (Moleon et al. 2015). 
Larger carcasses tend to last longer and also present a more conspicuous target for a foraging scavenger which results in more species attending them (Moleon et al. 2015).
This will have had implications for extinct assemblages because body size distributions vary across different environments but also across time. 
O'Gorman \& Hone (2012) showed Mesozoic faunal distributions may have been skewed towards larger species even when fossil biases are taken into account. 
Similarly, the megafauna of the Pleistocene (Doughty et al. 2013) would have produced large carcasses. 
As a result, the scavenger assemblages during this era would have been particularly diverse.''}}

@@

\item{ABSTRACT:} You could remove ``, the first to our knowledge''.

\textcolor{blue}{This has been removed.}

\item{ABSTRACT:} Also, you could mention some relevant specific findings of your synthesis.

\textcolor{blue}{We have added a final line to our abstract giving some specific findings: \textit{``Our approach offers, among others, an explanation as to why extinct pterosaurs likely scavenged and why extant bats don't.''}}

@@

\item{THE CHALLENGES OF SCAVENGING:} Page 3, 1st sentence: ``often difficult to predict'' compared to what? Please specify. There are many examples in which carrion is highly predictable, e.g., during salmon spawning (see also Pereira et al. 2014).

\textcolor{blue}{This passage has been removed from the section and later on in the paper we note that: \textit{``Carrion can often be unpredictable, such as in cases where animals succumb to disease''}}

@@

\item{LOCOMOTION:} Page 9, top paragraph: please be more cautious in your assertion, as cooperation skills and tools of early hominins probably allowed them to defend and usurp carcasses from more powerful scavengers.

\textcolor{blue}{We have changed this paragraph and take into account the authors' reference to tool use and sociality in hominins. The point is that even with these advantages, running to a carcass over long distances still wasn't energetically sensible.}

\item{DETECTION:} Page 11, top and 2nd paragraph, 1st sentence: this is about facilitation. As said above, facilitative processes may affect other parameters as well, not only the ability to detect carrion.

\textcolor{blue}{Facilitation is now considered throughout the manuscript.}

@@

\item{DETECTION:} Page 11, last sentence: explain why wind speed affects the olfactory capacity of an aquatic species.

\textcolor{blue}{We have added a section explaining why this is so: \textit{``wind speed determined the number of sharks feeding at whale carcasses due to chemical stimului from the carcasses being propogated through the water by the wind, indicating they were dependent on detecting the odours from the decaying whales.''}}

@@

\item{PREY AVAILABILITY:} I'd change this title to ``Carcass Availability'', which is more specific.

\textcolor{blue}{This has been changed.}

\item{PREY AVAILABILITY:} Among the different components of carcass availability, e.g., abundance, duration, predictability and accessibility, in this section you only talk about abundance and duration. You should also discuss about carcass predictability (e.g., see Cort\'{e}s-Avizanda et al. 2012) and carcass accessibility (e.g., see DeVault \& Krochmal 2002).

\textcolor{blue}{We now discuss all 4 aspects e.g. \textit{``Notably, freezing carcasses can become too hard to consume by most vertebrate carnviores (Selva et al 2003)''} and \textit{``Spikes in temperature can result in severe droughts causing mass mortality events which result in relatively predictable peaks in carrion availability (Kendall et al. 2014).''}}

@@

\item{PREY AVAILABILITY:} Page 13, 3rd and 4th sentences: whaling has exerted also a huge negative impact on scavengers by depleting whale populations. If you are going to talk about human impacts, maybe is better to do it at the end of the ms, perhaps in a new section in which you explore which scavenging traits could be more successful in a human dominated world.

\textcolor{blue}{We have decided to remove this section because we felt human impacts go beyond the scope of our paper.}

\item{PREY AVAILABILITY:} You should also take into account facilitative processes. For instance, some scavengers are able to access the interior of carcasses only once other, more powerful species, has opened the skin (see Mole\'{o}n et al. 2014 Biol. Rev.).

\textcolor{blue}{Our paper now references the literature on the facilitative processes involved in scavenging.}

@@

\item{FOOD PROCESSING:} Page 18, 3rd sentence: ``thus''? I don't understand this sentence; could you please reword it?

\textcolor{blue}{We have reworded this sentence. The idea is that early birds didn't have beaks and so could more easily eat meat. This is in contrast to modern birds where a beak may be a hindrance.}

\item{FOOD PROCESSING:} Page 18, 5th sentence: ``The mix of strong and weak features in their skull morphology''; please explain it.

\textcolor{blue}{We now note that their \textit{``skull morphologies and neck musculature are indicative of animals that were suited to removing large amounts of flesh from an immobile foodstuff (Witton 2013)''.}}
